---
title: "hw 12.5.1"
author: "siyu"
date: "2023-02-23"
output: html_document
---

```{r}
library(tidyverse)
```

```{r}
stocks <- tibble(
  year   = c(2015, 2015, 2015, 2015, 2016, 2016, 2016),
  qtr    = c(   1,    2,    3,    4,    2,    3,    4),
  return = c(1.88, 0.59, 0.35,   NA, 0.92, 0.17, 2.66)
)
stocks
```

```{r}
stocks%>%
  pivot_wider(names_from = year, values_from = return)%>%
  pivot_longer(
    cols = c(`2015`, `2016`),
    names_to = "year",
    values_to = "return",
    values_drop_na = TRUE
  )
```

```{r}
stocks%>%
  complete(year, qtr)
```

```{r}
treatment <- tribble(
  ~ person,           ~ treatment, ~response,
  "Derrick Whitmore", 1,           7,
  NA,                 2,           10,
  NA,                 3,           9,
  "Katherine Burke",  1,           4
)
treatment
```

```{r}
treatment%>%
  fill(person)
```

12.5.1 HW
1. 
Fill() takes a set of columns where you want missing values to be replaced by the most recent non-missing value (sometimes called last observation carried forward). 

Complete() takes a set of columns, and finds all unique combinations. It then ensures the original dataset contains all those values, filling in explicit NAs where necessary.

Pivot_wider() makes the table wider. Instead of having R complete or fill in the blanks for you, you have to call specific values and columns and do it "manually". 

2. 
The direction argument fill() decides what value fills the N/A vale (up(), down()...). 
